\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-12-02 paper.qmd
initial scdeed intro

>>>>

Motivated by this challenge, we present a statistical method, scDEED, for detecting dubious cell embeddings output by a 2D-embedding method. By calculating a reliability score for every cell embedding based on the similarity between the cell’s 2D-embedding neighbors and pre-embedding neighbors, scDEED identifies the cell embeddings with low reliability scores as dubious and those with high reliability scores as trustworthy. Moreover, by minimizing the number of dubious cell embeddings, scDEED provides intuitive guidance for optimizing the hyperparameters of an embedding method.

### 2024-12-02 paper.tex
initial scdeed intro

>>>>

Motivated by this challenge, we present a statistical method, scDEED,
for detecting dubious cell embeddings output by a 2D-embedding method.
By calculating a reliability score for every cell embedding based on the
similarity between the cell's 2D-embedding neighbors and pre-embedding
neighbors, scDEED identifies the cell embeddings with low reliability
scores as dubious and those with high reliability scores as trustworthy.
Moreover, by minimizing the number of dubious cell embeddings, scDEED
provides intuitive guidance for optimizing the hyperparameters of an
embedding method.
